---
title: "Data Analysis for Hospitals"
output: html_notebook
---

0. Libraries
```{r libraries}
library(tidyverse)
```


1. Upload data
```{r upload_data1}
general <- read.csv("~/PycharmProjects/Data Analysis for Hospitals/Data Analysis for Hospitals/task/test/general.csv")
general %>% head()
```

```{r upload_data2}
prenatal <- read.csv("~/PycharmProjects/Data Analysis for Hospitals/Data Analysis for Hospitals/task/test/prenatal.csv")
prenatal %>% head()
```


```{r upload_data3}
sports <- read.csv("~/PycharmProjects/Data Analysis for Hospitals/Data Analysis for Hospitals/task/test/sports.csv")
sports %>% head()
```

2. Rename column names and merge data
```{r merge_data}
data <- general %>% dplyr::bind_rows(
  prenatal %>% dplyr::rename('hospital'=HOSPITAL, 'gender'=Sex) %>% dplyr::bind_rows(
    sports %>% dplyr::rename('hospital'=Hospital, 'gender'=Male.female)
    )
  ) %>% dplyr::select(-X)
data %>% head()
```

3. Delete all the empty rows, replace NaN values in the gender column of the prenatal hospital with f and replace the NaN values in the bmi, diagnosis, blood_test, ecg, ultrasound, mri, xray, children, months columns with zeros.
```{r}

# data %>% dplyr::filter_all(all_vars(is.na(.) | .==''))  # select all empty rows
data <- data %>% dplyr::filter(! hospital == '')
# correct the gender
data$gender <- ifelse (data$gender=='female' | data$gender=='woman' | data$gender=='' | is.na(data$gender), 'f', 'm')
# replace all others missing values with 0
data[is.na(data) | data == ""] <- 0
data %>% head()
```

* Distribution on patients by hospital
```{r hospital_distribution}
data %>% dplyr::group_by(hospital) %>% dplyr::count()
ggplot(data) + geom_bar(mapping = aes(hospital))
```

* Distribution of diagnosis in the sports hospital
```{r sport_diagnosis}
diagnosis <- data %>% dplyr::filter(hospital == 'sports') %>% dplyr::group_by(diagnosis) %>% dplyr::count()
diagnosis
pie(x = diagnosis$n, labels = diagnosis$diagnosis)
```
* Difference in median age between general hospital and sports hospital
```{r}
data %>% dplyr::filter(hospital =='general' | hospital == 'sports') %>% dplyr::group_by(hospital) %>% dplyr::summarise(age_med = median(age))
```

* violin plot of growth distribution by hospitals
```{r}
ggplot(data) + geom_violin(mapping = aes(x = hospital, y = height))
```

